04_DESeq2

### 2020-08-28 analysis/boneyard/04_DESeq2.Rmd
cleaner repo

colData <- colData %>%
  mutate(external = fct_collapse(treatment,
                                 eggs = c("lay", "inc.d3", "inc.d9", "inc.d17", "prolong"),
                                 chicks = c("hatch", "n5", "n9", "extend" , "early" ),
                                 nest = c("bldg", "m.inc.d3",  "m.inc.d9",  "m.inc.d17",  "m.n2"),
                                 control = c("control"))) %>%
  drop_na()

colD
```

@@

```{r hypothesis, eval = F, message = F, warning = F}

@@

  createDEGdfhypothesis("hiloPRL", "hi", "lo", i)
  createDEGdfhypothesis("external", "chicks", "eggs", i)
  createDEGdfhypothesis("external", "chicks", "nest", i)
  createDEGdfhypothesis("external", "eggs", "nest", i)

>>>>

colData <- colData %>%
  mutate(external = fct_collapse(treatment,
                                 eggs = c("lay", "inc.d3", "inc.d9", "inc.d17", "prolong"),
                                 chicks = c("hatch", "n5", "n9", "extend" , "early" ),
                                 nest = c("bldg", "m.inc.d3",  "m.inc.d9",  "m.inc.d17",  "m.n2"),
                                 control = c("control"))) %>%
  drop_na()
```

@@

```{r hypothesis,  message = F, warning = F}

@@

  #createDEGdfhypothesis("hiloPRL", "hi", "lo", i)
  #createDEGdfhypothesis("external", "chicks", "eggs", i)
  #createDEGdfhypothesis("external", "chicks", "nest", i)
  #createDEGdfhypothesis("external", "eggs", "nest", i)
